Constructive Preference Elicitation by Setwise Max-margin Learning

### 2016-01-21 paper/ijcai16.tex
paper: update figures.

\begin{figure}[b]
    \centering
    \begin{tabular}{cccc}
        {\bf synthetic 3} & {\bf synthetic 4} & {\bf synthetic 5} & {\bf synthetic 6}
        \\
        \includegraphics[width=12em]{figures/synthetic_3_uniform_cv5_loss} &
        \includegraphics[width=12em]{figures/synthetic_4_uniform_cv5_loss} &
        \includegraphics[width=12em]{figures/synthetic_5_uniform_cv5_loss} &
        \includegraphics[width=12em]{figures/synthetic_6_uniform_cv5_loss}
        \\
        \includegraphics[width=12em]{figures/synthetic_3_uniform_sparse_cv5_loss} &
        \includegraphics[width=12em]{figures/synthetic_4_uniform_sparse_cv5_loss} &
        \includegraphics[width=12em]{figures/synthetic_5_uniform_sparse_cv5_loss} &
        \includegraphics[width=12em]{figures/synthetic_6_uniform_sparse_cv5_loss}
        \\
        \includegraphics[width=12em]{figures/synthetic_3_normal_cv5_loss} &
        \includegraphics[width=12em]{figures/synthetic_4_normal_cv5_loss} &
        \includegraphics[width=12em]{figures/synthetic_5_normal_cv5_loss} &
        \includegraphics[width=12em]{figures/synthetic_6_normal_cv5_loss}
        \\
        \includegraphics[width=12em]{figures/synthetic_3_normal_sparse_cv5_loss} &
        \includegraphics[width=12em]{figures/synthetic_4_normal_sparse_cv5_loss} &
        \includegraphics[width=12em]{figures/synthetic_5_normal_sparse_cv5_loss} &
        \includegraphics[width=12em]{figures/synthetic_6_normal_sparse_cv5_loss}
    \end{tabular}
    \caption{Results on the synthetic dataset, with crossvalidation every 5 steps. Each row represents a different
    setting: uniform, uniform sparse, normal, normal sparse. Color indicates
    the set size $k$: orange means $k=2$, blue $k=3$, and violet $k=4$.}
\end{figure}

\begin{figure}[b]
    \centering
    \begin{tabular}{cccc}
        {\bf synthetic 3} & {\bf synthetic 4} & {\bf synthetic 5} & {\bf synthetic 6}
        \\
        \includegraphics[width=12em]{figures/synthetic_3_uniform_cv5_time} &
        \includegraphics[width=12em]{figures/synthetic_4_uniform_cv5_time} &
        \includegraphics[width=12em]{figures/synthetic_5_uniform_cv5_time} &
        \includegraphics[width=12em]{figures/synthetic_6_uniform_cv5_time}
        \\
        \includegraphics[width=12em]{figures/synthetic_3_uniform_sparse_cv5_time} &
        \includegraphics[width=12em]{figures/synthetic_4_uniform_sparse_cv5_time} &
        \includegraphics[width=12em]{figures/synthetic_5_uniform_sparse_cv5_time} &
        \includegraphics[width=12em]{figures/synthetic_6_uniform_sparse_cv5_time}
        \\
        \includegraphics[width=12em]{figures/synthetic_3_normal_cv5_time} &
        \includegraphics[width=12em]{figures/synthetic_4_normal_cv5_time} &
        \includegraphics[width=12em]{figures/synthetic_5_normal_cv5_time} &
        \includegraphics[width=12em]{figures/synthetic_6_normal_cv5_time}
        \\
        \includegraphics[width=12em]{figures/synthetic_3_normal_sparse_cv5_time} &
        \includegraphics[width=12em]{figures/synthetic_4_normal_sparse_cv5_time} &
        \includegraphics[width=12em]{figures/synthetic_5_normal_sparse_cv5_time} &
        \includegraphics[width=12em]{figures/synthetic_6_normal_sparse_cv5_time}
    \end{tabular}
    \caption{Results on the synthetic dataset, with crossvalidation every 5 steps. Each row represents a different
    setting: uniform, uniform sparse, normal, normal sparse. Color indicates
    the set size $k$: orange means $k=2$, blue $k=3$, and violet $k=4$.}
\end{figure}

\begin{figure}[b]
    \centering
    \begin{tabular}{cc}
        {\bf loss} & {\bf time}
        \\
        \multicolumn{2}{c}{{\bf uniform sparse (no costs)}}
        \\
        \includegraphics[width=12em]{figures/pc_no_costs_uniform_sparse_cv5_loss} &
        \includegraphics[width=12em]{figures/pc_no_costs_uniform_sparse_cv5_time}
        \\
        \multicolumn{2}{c}{{\bf normal sparse (no costs)}}
        \\
        \includegraphics[width=12em]{figures/pc_no_costs_normal_sparse_cv5_loss} &
        \includegraphics[width=12em]{figures/pc_no_costs_normal_sparse_cv5_time}
        \\
        \multicolumn{2}{c}{{\bf uniform sparse (with costs)}}
        \\
        \includegraphics[width=12em]{figures/pc_with_costs_uniform_sparse_cv5_loss} &
        \includegraphics[width=12em]{figures/pc_with_costs_uniform_sparse_cv5_time}
        \\
        \multicolumn{2}{c}{{\bf normal sparse (with costs)}}
        \\
        \includegraphics[width=12em]{figures/pc_with_costs_normal_sparse_cv5_loss} &
        \includegraphics[width=12em]{figures/pc_with_costs_normal_sparse_cv5_time}
    \end{tabular}
    \caption{Results for the PC dataset with and without costs.}
\end{figure}

>>>>

\begin{figure}[b]
    \centering
    {\footnotesize
    \begin{tabular}{cccc}
        \hline
        {\sc synthetic 3} & {\sc synthetic 4} & {\sc synthetic 5} & {\sc synthetic 6}
        \\
        \hline \hline
        \multicolumn{4}{c}{{\sc Uniform}}
        \\
        \includegraphics[width=10em]{figures/synthetic_3_uniform_per_iter_loss} &
        \includegraphics[width=10em]{figures/synthetic_4_uniform_per_iter_loss} &
        \includegraphics[width=10em]{figures/synthetic_5_uniform_per_iter_loss} &
        \includegraphics[width=10em]{figures/synthetic_6_uniform_per_iter_loss}
        \\
        \hline
        \multicolumn{4}{c}{{\sc Uniform Sparse}}
        \\
        \includegraphics[width=10em]{figures/synthetic_3_uniform_sparse_per_iter_loss} &
        \includegraphics[width=10em]{figures/synthetic_4_uniform_sparse_per_iter_loss} &
        \includegraphics[width=10em]{figures/synthetic_5_uniform_sparse_per_iter_loss} &
        \includegraphics[width=10em]{figures/synthetic_6_uniform_sparse_per_iter_loss}
        \\
        \hline
        \multicolumn{4}{c}{{\sc Normal}}
        \\
        \includegraphics[width=10em]{figures/synthetic_3_normal_per_iter_loss} &
        \includegraphics[width=10em]{figures/synthetic_4_normal_per_iter_loss} &
        \includegraphics[width=10em]{figures/synthetic_5_normal_per_iter_loss} &
        \includegraphics[width=10em]{figures/synthetic_6_normal_per_iter_loss}
        \\
        \hline
        \multicolumn{4}{c}{{\sc Normal Sparse}}
        \\
        \includegraphics[width=10em]{figures/synthetic_3_normal_sparse_per_iter_loss} &
        \includegraphics[width=10em]{figures/synthetic_4_normal_sparse_per_iter_loss} &
        \includegraphics[width=10em]{figures/synthetic_5_normal_sparse_per_iter_loss} &
        \includegraphics[width=10em]{figures/synthetic_6_normal_sparse_per_iter_loss}
        \\
        \hline
    \end{tabular}
    }
\end{figure}

\begin{figure}[b]
    \centering
    {\footnotesize
    \begin{tabular}{cccc}
        \hline
        {\sc synthetic 3} & {\sc synthetic 4} & {\sc synthetic 5} & {\sc synthetic 6}
        \\
        \hline \hline
        \multicolumn{4}{c}{{\sc Uniform}}
        \\
        \includegraphics[width=10em]{figures/synthetic_3_uniform_per_query_loss} &
        \includegraphics[width=10em]{figures/synthetic_4_uniform_per_query_loss} &
        \includegraphics[width=10em]{figures/synthetic_5_uniform_per_query_loss} &
        \includegraphics[width=10em]{figures/synthetic_6_uniform_per_query_loss}
        \\
        \hline
        \multicolumn{4}{c}{{\sc Uniform Sparse}}
        \\
        \includegraphics[width=10em]{figures/synthetic_3_uniform_sparse_per_query_loss} &
        \includegraphics[width=10em]{figures/synthetic_4_uniform_sparse_per_query_loss} &
        \includegraphics[width=10em]{figures/synthetic_5_uniform_sparse_per_query_loss} &
        \includegraphics[width=10em]{figures/synthetic_6_uniform_sparse_per_query_loss}
        \\
        \hline
        \multicolumn{4}{c}{{\sc Normal}}
        \\
        \includegraphics[width=10em]{figures/synthetic_3_normal_per_query_loss} &
        \includegraphics[width=10em]{figures/synthetic_4_normal_per_query_loss} &
        \includegraphics[width=10em]{figures/synthetic_5_normal_per_query_loss} &
        \includegraphics[width=10em]{figures/synthetic_6_normal_per_query_loss}
        \\
        \hline
        \multicolumn{4}{c}{{\sc Normal Sparse}}
        \\
        \includegraphics[width=10em]{figures/synthetic_3_normal_sparse_per_query_loss} &
        \includegraphics[width=10em]{figures/synthetic_4_normal_sparse_per_query_loss} &
        \includegraphics[width=10em]{figures/synthetic_5_normal_sparse_per_query_loss} &
        \includegraphics[width=10em]{figures/synthetic_6_normal_sparse_per_query_loss}
        \\
        \hline
    \end{tabular}
    }
\end{figure}

\begin{figure}[b]
    \centering
    {\footnotesize
    \begin{tabular}{cccc}
        \hline
        {\sc synthetic 3} & {\sc synthetic 4} & {\sc synthetic 5} & {\sc synthetic 6}
        \\
        \hline \hline
        \multicolumn{4}{c}{{\sc Uniform}}
        \\
        \includegraphics[width=10em]{figures/synthetic_3_uniform_per_iter_time} &
        \includegraphics[width=10em]{figures/synthetic_4_uniform_per_iter_time} &
        \includegraphics[width=10em]{figures/synthetic_5_uniform_per_iter_time} &
        \includegraphics[width=10em]{figures/synthetic_6_uniform_per_iter_time}
        \\
        \hline
        \multicolumn{4}{c}{{\sc Uniform Sparse}}
        \\
        \includegraphics[width=10em]{figures/synthetic_3_uniform_sparse_per_iter_time} &
        \includegraphics[width=10em]{figures/synthetic_4_uniform_sparse_per_iter_time} &
        \includegraphics[width=10em]{figures/synthetic_5_uniform_sparse_per_iter_time} &
        \includegraphics[width=10em]{figures/synthetic_6_uniform_sparse_per_iter_time}
        \\
        \hline
        \multicolumn{4}{c}{{\sc Normal}}
        \\
        \includegraphics[width=10em]{figures/synthetic_3_normal_per_iter_time} &
        \includegraphics[width=10em]{figures/synthetic_4_normal_per_iter_time} &
        \includegraphics[width=10em]{figures/synthetic_5_normal_per_iter_time} &
        \includegraphics[width=10em]{figures/synthetic_6_normal_per_iter_time}
        \\
        \hline
        \multicolumn{4}{c}{{\sc Normal Sparse}}
        \\
        \includegraphics[width=10em]{figures/synthetic_3_normal_sparse_per_iter_time} &
        \includegraphics[width=10em]{figures/synthetic_4_normal_sparse_per_iter_time} &
        \includegraphics[width=10em]{figures/synthetic_5_normal_sparse_per_iter_time} &
        \includegraphics[width=10em]{figures/synthetic_6_normal_sparse_per_iter_time}
        \\
        \hline
    \end{tabular}
    }
\end{figure}

\begin{figure}[b]
    \centering
    {\footnotesize
    \begin{tabular}{cccc}
        \hline
        {\sc synthetic 3} & {\sc synthetic 4} & {\sc synthetic 5} & {\sc synthetic 6}
        \\
        \hline \hline
        \multicolumn{4}{c}{{\sc Uniform}}
        \\
        \includegraphics[width=10em]{figures/synthetic_3_uniform_per_query_time} &
        \includegraphics[width=10em]{figures/synthetic_4_uniform_per_query_time} &
        \includegraphics[width=10em]{figures/synthetic_5_uniform_per_query_time} &
        \includegraphics[width=10em]{figures/synthetic_6_uniform_per_query_time}
        \\
        \hline
        \multicolumn{4}{c}{{\sc Uniform Sparse}}
        \\
        \includegraphics[width=10em]{figures/synthetic_3_uniform_sparse_per_query_time} &
        \includegraphics[width=10em]{figures/synthetic_4_uniform_sparse_per_query_time} &
        \includegraphics[width=10em]{figures/synthetic_5_uniform_sparse_per_query_time} &
        \includegraphics[width=10em]{figures/synthetic_6_uniform_sparse_per_query_time}
        \\
        \hline
        \multicolumn{4}{c}{{\sc Normal}}
        \\
        \includegraphics[width=10em]{figures/synthetic_3_normal_per_query_time} &
        \includegraphics[width=10em]{figures/synthetic_4_normal_per_query_time} &
        \includegraphics[width=10em]{figures/synthetic_5_normal_per_query_time} &
        \includegraphics[width=10em]{figures/synthetic_6_normal_per_query_time}
        \\
        \hline
        \multicolumn{4}{c}{{\sc Normal Sparse}}
        \\
        \includegraphics[width=10em]{figures/synthetic_3_normal_sparse_per_query_time} &
        \includegraphics[width=10em]{figures/synthetic_4_normal_sparse_per_query_time} &
        \includegraphics[width=10em]{figures/synthetic_5_normal_sparse_per_query_time} &
        \includegraphics[width=10em]{figures/synthetic_6_normal_sparse_per_query_time}
        \\
        \hline
    \end{tabular}
    }
\end{figure}

\begin{figure}[b]
    \centering
    {\footnotesize
    \begin{tabular}{cccc}
        \hline
        \multicolumn{4}{c}{{\sc uniform sparse}}
        \\
        \multicolumn{2}{c}{{\sc loss/time per iteration}} &
        \multicolumn{2}{c}{{\sc loss/time per query}}
        \\
        \includegraphics[width=10em]{figures/pc_with_costs_uniform_sparse_per_iter_loss} &
        \includegraphics[width=10em]{figures/pc_with_costs_uniform_sparse_per_iter_time} &
        \includegraphics[width=10em]{figures/pc_with_costs_uniform_sparse_per_query_loss} &
        \includegraphics[width=10em]{figures/pc_with_costs_uniform_sparse_per_query_time}
        \\
        \hline
        \multicolumn{4}{c}{{\sc normal sparse}}
        \\
        \multicolumn{2}{c}{{\sc loss/time per iteration}} &
        \multicolumn{2}{c}{{\sc loss/time per query}}
        \\
        \includegraphics[width=10em]{figures/pc_with_costs_normal_sparse_per_iter_loss} &
        \includegraphics[width=10em]{figures/pc_with_costs_normal_sparse_per_iter_time} &
        \includegraphics[width=10em]{figures/pc_with_costs_normal_sparse_per_query_loss} &
        \includegraphics[width=10em]{figures/pc_with_costs_normal_sparse_per_query_time}
        \\
        \hline
    \end{tabular}
    }
    \caption{Results for the PC dataset.}
\end{figure}
